Modeling the impacts of replacing car trips with combined public transport and cycling: \ Reproducible methods, results and actionable evidence from the biclaR project

### 2023-11-28 paper/PaperCEUS/PaperCEUS.Rmd
Beef-up results

Our findings suggest that cycling *in combination* with PT could potentially replace 10% of current LMA trips, with an additional 6% of PT journeys prone to further substitution. 
<!-- repeated? -->

>>>>

Our findings show that cycling *in combination* with PT could replace 10% of current LMA trips, with an additional 6% of PT journeys prone to further substitution, based on conservative assumptions.
